---
title: "RWorksheet_TAN#4"
author: "John Kenneth D. Tan"
date: "2022-11-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. The table below shows the data about shoe size and height. 
Create a data frame.
```{r  df}
table_data <- data.frame(
  Shoesize = c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 
               13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 
               11.5, 8.5, 5.0, 10.0, 6.5 ,7.5, 8.5, 10.5,
               8.5, 10.5, 11.0, 9.0, 13.0),
  
  Height = c(66.0, 68.0, 64.0, 65.0, 70.0, 64.0, 70.0, 71.0, 
             72.0, 64.0, 74.0, 67.0, 71.0, 71.0, 77.0, 72.0, 
             59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 
             72.0, 70.0, 69.0, 70.0),
  
  Gender = c("F","F","F","F","M","F","F","F","M","F","M","F",
             "M","M","M","M","F","F","M","F","F", "M","M","F",
             "M","M","M","M"))

names(table_data)<-list("Shoe size", "Height", "Gender")

table_data
```
  a. Describe the data.

Answer: The data is composed of three columns and 28 rows that 
contains the Shoe size, Height and Gender.

  b. Find the mean of shoe size and height of the respondents.
  Copy the codes and results
  
```{r   shoesize}
Shoesize <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 
             11.5, 8.5, 5.0, 10.0, 6.5 ,7.5, 8.5, 10.5 ,8.5, 10.5, 11.0, 9.0, 13.0)
Shoesize

mean_Shoesize <- mean(Shoesize)
mean_Shoesize
```
```{r  height}
Height <- c(66.0, 68.0, 64.0, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.0, 67.0, 71.0, 71.0, 
           77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
Height

mean_height <- mean(Height)
mean_height
```
  c. Is there a relationship between shoe size and height? Why?

Yes, when the respondents are tall, their shoe sizes are also big. Whereas, if their height is below 70.0, their shoe size are smaller.

\hfill\break
2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.

```{r  fmv}
months_vector <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August",
"July","December","August","August","September","November","February","April")

factor_months_vector <- factor(months_vector)
factor_months_vector
```
\hfill\break
3. Then check the summary() of the months_vector and factor_months_vector. 
#Interpret the results of both vectors. Are they both equally useful in this case?
```{r summary} 
  summary(months_vector)
  summary(factor_months_vector)
```
Answer: Yes, it is beneficial because it aids in the efficient understanding of data. In months_vector, you do not need to count the number of words because of the function length. Its mode and class are also displayed. You don't have also to manually count the number of times a specific month appears in factor_months_vector because it's already computed.

\hfill\break 
4. Create a vector and factor for the table below.
```{r  fac_data}  
  factor_data <- c("East" = '1', "West" = '4', "North" = '3')
  factor_data
```

\hfill\break
5. Enter the data below in Excel with file name = import_march.csv

  a. Import the excel file into the Environment Pane using         read.table() function. Write the code.
```{r  excel} 
 setwd("C:/Users/Kenneth/Desktop/RProg_Worksheets/Worksheet  4/")
 
 import_table<-read.table("import_march.csv", header=TRUE, sep=",")
 import_table 
```
  b. View the dataset. Write the code and its result.
```{r  view_data} 
  view_data<- read.csv("import_march.csv")
  view_data
```
