---
title: "Worksheet-2 in R"
author: "John Kenneth D. Tan"
date: "2022-10-06"
output: pdf_document
---
Tan, John Kenneth D.  BSIT 2-A


1. Create a vector using : operator

a.	Sequence from -5 to 5. 
Write the R code and its output. Describe its output.

```{r vec1a}
NumSeq<- c(-5:5)
NumSeq
```
A sequence from -5 to 5 is stored in the object called NumSeq and was displayed.

b.	x <- 1:7. What will be the value of x?

```{r vec1b}
x <- 1:7
x
```

\hfill\break

2. Create a vector using seq() function
a. seq(1, 3, by=0.2) #specify step size
Write the R code and its output. Describe the output.

```{r vec2}
seq_data <- seq(1, 3, by=0.2)
seq_data
```
The gap of these numbers in the sequence was 0.2.

\hfill\break

3. A factory has a census of its workers. There are 50 workers in total. The following list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.
```{r vec3}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 
         57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 
         18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26,18)
age
```
a.	Access 3rd element, what is the value?
```{r vec3a}  
  third_element <- c(age[3])
  third_element
```

b.	Access 2nd and 4th element, what are the values?
```{r vec3b}
second_and_fourth_element <-age[c(2,4)]
second_and_fourth_element
```

c.	Access all but the 1st element is not included. Write the R code and its output.
```{r vec3c}
all_element <- age[c(2:50)]
all_element
```
\hfill\break

4.	*Create a vector x <- c("first"=3, "second"=0, "third"=9). Then named the vector, names(x).

a.	Print the results. Then access x[c("first", "third")]. Describe the output.
```{r vec4a}
names<- c("first"=3, "second"=0, "third"=9)
names
```
```{r vec4a.1}
names <-names [c("first","third")]
names
```
The first with the value of 3 and third with a value of 9 were accessed. Therefore
the second with a value of 0 didn't displayed.

b.	Write the code and its output.
```{r vec4b}
names<- c("first"=3, "second"=0, "third"=9)
names
```
```{r vec4b.1}
names <-names [c("first","third")]
names
```

\hfill\break

5. Create a sequence x from -3:2.

a. Modify 2nd element and change it to 0;

```{r vec5a}
x<- c(-3:2)
x
```
```{r vec5a1}
x[2] <- 0
x
```

Describe the output:
The second element which is -2 was changed to 0

\hfill\break

6.	The following data shows the diesel fuel purchased by Mr. Cruz.

a. Create a data frame for month, price per liter (php) and purchase-quantity (liter).
Write the codes.
```{r vec6a}
Diesel_Fuel<- data.frame(
  Month = c("Price per liter (PhP)", "Purchase-quantity(Liter)"),
   Jan = c(52.50, 25),
   Feb = c(57.25, 30),
   March = c(60.00, 40),
   Apr = c(65.00, 50),
   May = c(74.25, 10),
   June = c(54.00, 45)
)
Diesel_Fuel
```  
b. What is the average fuel expenditure of Mr. Cruz from Jan to June? Note: Use
weighted.mean(liter, purchase)
```{r vec6b}
liter<-c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
purchase<-c(25,30,40,50,10,45)
weighted.mean(liter, purchase)
```
\hfill\break

7. R has actually lots of built-in datasets. For example, the rivers data “gives the lengths
(in miles) of 141 “major” rivers in North America, as compiled by the US Geological Survey”.

a. Type “rivers” in your R console. Create a vector data with 7
elements, containing the number of elements (length) in rivers,
their sum (sum), mean (mean), median (median), variance (var)
standard deviation (sd), minimum (min) and maximum (max).
```{r vec7}
rivers
```

b. What are the results?
  
length = 141.0000
sum = 83357.0000 
mean =  591.1844
median = 425.0000
variance = 243908.4086
standard deviation = 493.8708 
minimum = 135.0000
maximum = 3710.0000
  
c. Write the code and its outputs.
```{r 7c}
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers),
          sd(rivers), min(rivers), max(rivers))
data
```

\hfill\break

8 a. Create vectors according to the above table. Write the codes.
```{r vec 8a}
Powerful_Celeb <- data.frame(
  Power_Ranking = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 
                    15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25), 
  Celebrity_Name = c("Tom cruise", "Rolling Stone", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg", 
                    "Howard Stem", "50 cents", "Cast of the Supranos", "Dan brown", "Bruce Springteen", "Donald Trump","Muhammad Ali",
                    "Paul McCartney", "Goerge Lucas", "Elton John", "David Letterman", "Phil Mickelson", "J.K Rowling", 
                    "Bradd Pitt", "Peter Jackson", "Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant"),
  Pay = c(67, 90, 225, 110 , 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31 )
)

Powerful_Celeb
```

b. Modify the power ranking and pay of J.K. Rowling. Change power ranking to 15 and
pay to 90. Write the codes and its output.

```{r vec8b}
Power_Ranking <- 1:25
CelebrityName <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", 
                   "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the sopranos",
                   "Dan Brown", "Bruce Springsteen", "Donald Trump", "Muhammad Ali", "Paul McCartney",
                   "George Lucas", "Elton John", "David Letterman", "Phil Mickelson", "J.K Rowling",
                   "Bradd Pitt", "Peter Jackson", "Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant")
Pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40,
         233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31)
```

```{r vec8b.2}
Power_Ranking [19] <- 15
Power_Ranking
Pay [19] <- 90
Pay
```

```{r vec8b.1}
Powerful_Celeb <- data.frame(Power_Ranking, CelebrityName, Pay)
Powerful_Celeb
```

c. Interpret the data.

Powerful_Celeb is the object used to store the ranking of powerful celebrities.
Through the data frame, their rankings are clearly shown vertically. Inside the object, 
PowerRanking, CelebrityName, and Pay are stored. After the successful display, J.K Rowling power ranking was modified to 15 and pay to 
change power ranking to 15 and pay to 90.



