---
title: 'Individual Project #2'
author: "John Kenneth D. Tan"
date: "2022-12-06"
output: html_document
---

Individual Project #2

Name: John Kenneth D. Tan
Course, Year & Section: BSIT 2-A


Libraries to be used/called out
```{r libraries}
library(dplyr)
library(twitteR)
library(tidytext)
library(rtweet)
library(RColorBrewer)
library(ggplot2)
```

1.Extract from twitter using your developer's credentials. Choose any keyword you want. 

Tokens and keys are needed. 
Check your Programs and Apps in the Developer’s Portal.
```{r  keys}
CONSUMER_SECRET <-"bmUGeGVHxLxtc63GAyEHo2DDaHpmmjeJyrZ3XPLSMRtvOY8xpW"
CONSUMER_KEY <- "dxIq4p3oOGBD9DM4sfw2JVcFh"
ACCESS_SECRET <- "YkZLrUJVHrwCh44s92O70XaYmLZWCHvIDick1T60wdH5v"
ACCESS_TOKEN <- "1594143309362270210-hApMHAP6C8nRlj9ipxEfzrnLBbrWcJ"
```

Connect to twitter app
```{r  connect_to_twitter}
setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```

2.Extract 10000 tweets from Twitter using twitteR package including retweets.
```{r  searchTwitter}
   Lisa_tweets = searchTwitter("Lalisa",
                               n=10000,
                               since = "2022-11-21",
                               until = "2022-11-28",
                               lang = "en",
                               retryOnRateLimit = 120)
```

Convert data into dataframe
```{r LisaDF}
Lisa_DF <- twListToDF(Lisa_tweets)
save(Lisa_DF,file = "Lisa_DF.Rdata")
#load(file = "Lisa_DF.Rdata")
```

Subsetting using the dplyr() package

Subset the organic tweets
```{r  organicTwts}
Lisa_OrigTwt <- subset(Lisa_DF, isRetweet == "FALSE",select =
                         c(text,screenName,created,isRetweet))
save(Lisa_OrigTwt, file = "Lisa_OrigTwt.Rdata")
#load(file="Lisa_OrigTwt.Rdata")
```
```{r  min_max1}
Lisa_OrigTwt %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

Lisa_OrigTwt %>% 
  mutate(Created_At_Round = created%>% 
           round(units = 'hours') %>% 
           as.POSIXct())

Lisa_OrigTwt %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

Lisa_OrigTwt %>% pull(created) %>% max()
```
Subset the retweets
```{r  retweets}
Lisa_subRT <- subset(Lisa_DF, isRetweet == "TRUE",select =
                      c(text,screenName,created,isRetweet))
save(Lisa_subRT, file = "Lisa_subRT.Rdata")
#load(file="Lisa_subRT.Rdata")
```

```{r min_max2}
Lisa_subRT %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

Lisa_subRT%>% 
  mutate(Created_At_Round = created%>% 
           round(units = 'hours') %>% 
           as.POSIXct())

Lisa_subRT %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

Lisa_subRT %>% pull(created) %>% max()
```

3.Plot the retweets and the original tweets using bar graph in vertical manner. Include legends.

a. Plotting of Organic tweets
```{r  plotTweets}
ggplot(data = Lisa_OrigTwt, aes(x = created), fill = Lisa_OrigTwt) +
  geom_histogram(aes(fill = ..count..)) + 
  theme(legend.position="right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 0, hjust = 1)) +
  xlab("Time") + ylab("Number of Organic tweets per Hour") + 
  scale_fill_gradient(low = "pink", high = "darkblue")
```

b. Plotting of Retweets
```{r  plotRetweets}
ggplot(data = Lisa_subRT, aes(x = created), fill = Lisa_subRT) +
  geom_histogram(aes(fill = ..count..)) + 
  theme(legend.position="right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 0, hjust = 1)) +
  xlab("Time") + ylab("Number of Reweets per Hour") + 
  scale_fill_gradient(low = "yellow", high = "red")
```

















