---
title: "RWorksheet_TAN#5."
author: "John Kenneth D. Tan"
date: "2022-11-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The table shows the enrollment of BS in Computer Science, SY 2010-2011.
```{r  enrollment_data}
enrollment_data<- data.frame (
  "Course Year" = c("1st","2nd","3rd","4th"),
  "2019-2020" = c(80,75,70,60)
)
enrollment_data
```
  a. Plot the data using a bar graph. Write the codes and copy the result.
require(ggplot2)
```{r  plot_data}
plot_data <- c("1st" = 80, "2nd" = 75, "3rd" = 70, "4th" = 60)
barplot(plot_data)
```

b. Using the same table, label the barchart with
Title = ” Enrollment of BS Computer Science
horizontal axis = “Curriculum Year” and
vertical axis = “number of students”
```{r barchart}
plot_data <- c("1st" = 80 , "2nd" = 75, "3rd" = 70, "4th" = 60)
barplot(plot_data, main = "Enrollment of BS Computer Science", xlab = 
          "Curriculum Year", ylab = "number of students")
```

2. The monthly income of De Jesus family was spent on the following: 60% on Food, 10% on electricity, 5% for savings, and 25% for other miscellaneous expenses.

  a. Create a table for the above scenario. Write the codes and its result.
```{r  df}
expenses_data <- data.frame(
  facts = c("Food", "Electricity", "Savings", "Miscellaneous_expenses"),
  spent = c(60, 10, 5, 25)
)
expenses_data
```

```{r  data_table}
table_data <- table(expenses_data)
table_data
```

  b. Plot the data using a pie chart. Add labels, colors and legend. 
  Write the codes and its result.
  
```{r  pie}
spent = c(60, 10, 5, 25)
data_per <- round(spent/sum(spent) * 100, 1)
data_per <- paste(data_per,"%",sep = " ")

data_pie <- pie(spent,
                main = "Month Data",
                col = rainbow(4),
                labels =  data_per, cex = 0.8)
                
data_pie
                
                legend("topright", c("Food","Electricity","Savings","Miscellaneous expenses"),
                       cex = 0.8,fill = rainbow(4))
                
```             
  3. Open the mtcars dataset.

  a. Create a simple histogram specifically for mpg (miles per gallon) variable. Use $ to select the mpg only. Write the codes and its result.
```{r cars} 
  data("mtcars")
  data_mtcars <- (mtcars$mpg)
  data_mtcars
                
  hist(data_mtcars, breaks = 5)
```
  
  b. Colored histogram with different number of bins. 
  hist(mtcars$mpg, breaks=12, col="red") 
  Note: breaks= controls the number of bins.
```{r  hist}
   hist(data_mtcars, breaks=12, col="red")
```

  c. Add a Normal Curve. 
  Copy the result. 
```{r  curve}   
   cars <- mtcars$mpg
   
   h<-hist(cars, breaks=10, col="red", xlab="Miles Per Gallon",
           main="Histogram with Normal Curve")
   
   xfit<-seq(min(cars),max(cars),length=40)
   yfit<-dnorm(xfit,mean=mean(cars),sd=sd(cars))
   yfit <- yfit*diff(h$mids[1:2])*length(cars)
   lines(xfit, yfit, col="blue", lwd=2)
   
h
```

  4. Open the iris dataset. Create a subset for each species.
 # a. Write the codes and its result.
```{r  iris_data} 
 data("iris")
 iris_data <- data.frame(iris)
 iris_data
 
 setosa_data <- subset(iris_data, Species == 'setosa' )
 setosa_data
 
 versicolor_data <- subset(iris_data, Species == 'versicolor' )
 versicolor_data
 
 virginica_data <- subset(iris_data, Species == 'virginica' )
 virginica_data
``` 

 # b. Get the mean for every characteristics of each species using colMeans(). 
 #Write the codes and its result. 
 #Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])
 
```{r  iris} 
 setosa <- colMeans(setosa_data[sapply(setosa_data,is.numeric)])
 setosa
 
 versicolor <- colMeans(versicolor_data[sapply(versicolor_data,is.numeric)])
 versicolor
 
 virginica <- colMeans(virginica_data[sapply(virginica_data,is.numeric)])
 virginica
```
 
 #c. Combine all species by using rbind()
 #The table should be look like this:
```{r  rbind}
data_iris <- rbind(setosa, versicolor,virginica)
data_iris

iris_df <- data.frame(data_iris)
iris_df
```
 
 
 
 #d. From the data in 4-c: Create the barplot().
 #Write the codes and its result.

```{r  bardf}
barplot(height=as.matrix(iris_df), beside = TRUE,
        main = "Iris Mean",
        xlab = "Characteristics",
        ylab = "Mean Score",
        col = rainbow(3))
``` 
  
  
                
