---
title: "RWorskheet_TAN#6"
author: "John Kenneth D. Tan"
date: "2022-11-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Worksheet #6
```{r  x}
library(ggplot2)
library(dplyr)
data(mpg)
datampg <- glimpse(mpg)
```

1. How many columns are in mpg dataset? How about the number of rows? Show the
codes and its result.

Number of columns in mpg data set
```{r  ncol}
ncol(mpg)
```
Number of rows in mpg data set
```{r nrow}
nrow(mpg)
```
\hfill\break
2. Which manufacturer has the most models in this data set? Which model has the most variations? 
```{r  most_models} 
manufac<-mpg%>%
group_by(manufacturer)%>%count()
manufac

colnames(manufac)<-c("Manufacturer", "Counts")
```
#Answer:
  Dodge is the manufacturer that has the most models, 
  for it has 37 models.
  
  a. Group the manufacturers and find the unique models. Copy     the codes and result.
```{r  unique}  
  unique_data <- mpg %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
  colnames(unique_data) <- c("Manufacturer", "Model","Counts")
  unique_data
```  

  b. Graph the result by using plot() and ggplot(). Write the     codes and its result.
```{r  grpdata}
  plot(unique_data)
```

```{r  groupdta}
  ggplot(unique_data, aes(Model, Manufacturer)) + geom_point()
``` 
\hfill\break
3. Same dataset will be used. You are going to show the relationship of the model and the manufacturer.

  a. What does ggplot(mpg, aes(model, manufacturer)+
  geom_point() show?
```{r  relationship}
  ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
  Answer: It connects the models to their appropriate             manufacturers through plotting it.
  
  b. For you, is it useful? If not, how could you modify the      data to make it more informative?
  
  Answer: It is useful because it arranges and organizes the      data, by that, it is easy to distinguish the relationship       between manafacturers and models.
  
\hfill\break
4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result.  
```{r  model}
  group_model <- unique_data %>% group_by(Model) %>% count()
  group_model
  colnames(group_model) <- c("Model","Counts")
  group_model
```

  a. Plot using the geom_bar() + coord_flip() just like what is   shown below. Show codes and its result
```{r  geom1}  
qplot(model,data = mpg,main = "Number of Cars 
per Model", xlab = "Model",ylab = "Number 
of Cars", geom = "bar", fill = manufacturer) + 
coord_flip()
```  
b. Use only the top 20 observations. Show code and results
```{r observation}
top_obs <- mpg %>% 
  group_by(model) %>% 
  tally(sort = TRUE)
top_obs
ggplot(top_obs, aes(x = model, y = n, fill = "rainbow")) +
  geom_bar(stat = "identity") + coord_flip()
``` 
\hfill\break
5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic colour = engine displacement. Title should be “Relationship between No. of Cylinders and Engine Displacement”.
  
  a. Show the codes and its result.
```{r  cyl_disp}  
  ggplot(data = mpg) + 
  geom_point(mapping = aes(y = cyl ,
    x = displ ,
    colour = 'engine displacement', 
    title = 'Relationship between No. of 
    Cylinders and Engine Displacement'))
```  
  
  
  b. How would you describe its relationship?
  
   Answer: Less cylinders means less inertia in the engine. As     the number of cyclinders increases, the number of engine
   displacement also increases.

\hfill\break  
6. Get the total number of observations for drv - type of drive train (f = front-wheel drive, r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.).
  
Plot using the geom_tile() where the number of observations for class be used as a fill for aesthetics.
  
  a. Show the codes and its result for the narrative in #6.
```{r  geom}  
  ggplot(data = mpg, mapping = aes(x = drv, y = class)) +         geom_tile(aes(fill=class))
```  
  b. Interpret the result.
  
  Answer: Under the 4 wheel drive are the suv, subcompact,        pick-up, midsize and compact. Then Mini van is only a front     wheel drive while 2seater is only a rear wheel drive.

\hfill\break
7. Discuss the difference between these codes. Its outputs for  each are shown below.
  Code #1
```{r  code1}  
  ggplot(data = mpg) +
    geom_point(mapping = aes(x = displ, y = hwy, colour = "red"))
```  
  
  Code #2
```{r code2}  
  ggplot(data = mpg) +
    geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```  
  Answer: The outputs are closely the same except for some minor   differences. Based on the output, they differ in color, one is   red and the other one is blue. The first one also has a legend   for its colour compared to the second one that has none.

\hfill\break    
8. Try to run the command ?mpg. What is the result of this command?
   
   ?mpg
    
  a. Which variables from mpg dataset are categorical?

Answer: Categorical variables in mpg include: manufacturer, model, trans (type of transmission), drv (front-wheel drive, rear-wheel, 4wd), fl (fuel type), and class (type of car).  
  
  b. Which are continuous variables?

Answer: doubles or integers  
    
  c. Plot the relationship between displ (engine displacement)      and hwy(highway miles per gallon). Mapped it with a             continuous variable you have identified in #5-b. What 
    is its result? Why it produced such output?
```{r displhwy}
ggplot(mpg, aes(x=displ, y=hwy, colour = cty)) +geom_point()    
```      
  Answer: The displ(engine displacement) and hwy(highway miles    per gallon) are matched together through mapping/plotting it    then the values are represented by the different shade of       color blue.

\hfill\break      
9. Plot the relationship between displ(engine displacement) and hwy(highway miles per gallon) using geom_point(). Add a trend line over the existing plot using geom_smooth() with se = FALSE. Default method is “loess”.
```{r  displ_hwy}  
  ggplot(data = mpg, mapping = aes(x = displ, 
  y = hwy)) + geom_point(mapping=aes(color=class))+
  geom_smooth(se = FALSE)
``` 

\hfill\break  
10. Using the relationship of displ and hwy, add a trend line over existing plot. Set these = FALSE to remove the confidence interval and method = lm to check for linear  modeling.
```{r plot}  
  ggplot(data = mpg, mapping = aes(x = displ, 
  y = hwy, color =    class)) + geom_point() + 
  geom_smooth(se = FALSE, method = lm)
```  